Query Optimization for Dynamic Imputation

### 2017-05-06 rebuttal.tex

\item D7. When defining the cost of impute operator, how do you know a priori the number of iterations for the algorithm (given it has to converge)?

\item D8. Are there impute implementation that are non-blocking? Or do they always have to perform multiple passes over the data?

\item D9. Additional experiments I suggest to include:
-- Consider a scenario where the user submits multiple similar queries. Show after how many such queries your approach has no longer a competitive advantage compared to performing imputation on the data.
-- Try different values for $\alpha$ (not just 0 and 1).
-- Show runtime of enumeration algorithm as queries get more complex.

\resp{
The sensitivity of different values of $\alpha$ depends on the query itself. Performing a scan of values of $\alpha$ with small step sizes can return
a lot of the same plans for execution. In lieu of this, we extended the results section to include a subsection that presents the final frontiers for
two queries, one from each dataset used during evaluation. This frontier can be exposed to the user to help in their workflow.
\\
We explored the planning times for queries with increasing number of joins. The standard algorithm presented in the original version submitted handles
up to 5 joins, with columns requiring imputation in all tables, with planning time of approximately one second. We added a small optimization to help reduce
planning times for a larger number of joins. We maintain an approximation of the Pareto sets, rather than the exact set, by only adding non-dominated plans that
are sufficiently different. This helps reduce some of the increases in planning time for a larger number of joins.}

### 2017-05-06 paper/experiments.tex
added plots of plan frontiers for queries 1 and 6 to paper and rebuttal

@@

>>>>

\Cref{fig:pareto-frontiers} shows the final Pareto frontiers produced for \Cref{q1} and \Cref{q6}. These are the resulting set of plans after pruning dominated plans throughout our algorithm.
The diversity of plans highlights the possible tradeoffs that the user can make in choosing a final plan for execution. The frontier is available at the end of the planning stage and
can be exposed to the user to help in guiding their workflow for exploring values of $\alpha$.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/pareto_frontiers_plot.png}
\caption{\ProjectName{}'s final Pareto frontier for \Cref{q1} and \Cref{q6}. The user can tradeoff between the plans by adjusting values of $\alpha$. Depending on the query
there may be small clusters of plans centered around a similar penalty or time value. The frontier is produced before executing a plan and can be exposed
to the user.}
\label{fig:pareto-frontiers}
\end{figure}
